Mathematical Models of Delta-Notch Signalling

### 2025-03-17 paper/paper.tex
Added hex grid figure paper.tex
Differentiation time analysis for two-cell models.

\newpage

@@

Let us define:\\
$P(n,d,i,t)$ = probability of having $n$ Notch receptors, $d$ Delta ligands, and $i$ NICD molecules at time $t$.\\

The Kolmogorov forward equation describes how $P(n,d,i,t)$ changes over a small time step $\Delta t$:

@@

>>>>

@@

Let us define $P(n,d,i,t)$ to be the probability of having $n$ Notch receptors, $d$ Delta ligands, and $i$ NICD molecules at time $t$. The Kolmogorov forward equation describes how $P(n,d,i,t)$ changes over a small time step $\Delta t$:

@@

\begin{figure}
  \includegraphics[width=\textwidth]{img/ODE_HexGrid.png}
  \caption{Results of the 8x8 hexagonal domain ODE model showing final Notch values per cell.}
\end{figure}
